Transparency in Science

### 2023-05-15 presentation.Rmd
add more slides
add points about ML roughly equal to preregistration

.large[ .highlight[Reproducibility] is a necessary* condition to estimate:]

@@

.transparent.small.right.grey[*In an ideal world.]

@@

>>>>

.large[ .highlight[Reproducibility] is a necessary condition to estimate:]

@@

.transparent[*In an ideal world.]

@@

.transparent.blurry2.large[about]

.transparent.huge.blurry2[

#.suppress.blurry2[Uncertainty]

.blurry2.large[about]

.highlight.huge.blurry2[

.large[
In .highlight[Machine Learning], $\mathcal{C}(\text{Model})$ is often unknown.
]

#.textgrey[Cross Validaton]

.right.large.transparent[**but resetting researchers memory is unethical]

.right.large.transparent[**impossible**]

#.textgrey[Cross Validaton]

.right.large[**but resetting researchers memory is ~~unethical~~**]

.right.large[**impossible**]

#.textgrey[Test-set]

$\mathcal{C}(\text{Model}) = 0$

# Preregistration

$\mathcal{C}(\text{Human}) = 0$

# Unconvential

# Explatory Preregistrations?

$\mathcal{C} = \mathcal{C}(\text{Model}) + \mathcal{C}(\text{Human})$

Preregistration: $\mathcal{C}(\text{Human}) = 0$

$\mathcal{C}(\text{Model})$ still might be high.

```{r}
results <- readr::read_rds(here::here("data", "simulation.rds")) 
```

```{r measure-plots}
# see R/plots.R
```

```{r}
p <- plots[["Posterior Probability"]] +
  xaringanthemer::theme_xaringan() +
    theme(legend.position = c(.2, .8),
        legend.title = element_blank(),
        text = element_text(size = 18, color = colors$red),
        title = element_blank(),
        axis.title = element_text(size = 18),
        plot.caption = element_text(size = 15)) +
  labs(x = "Exploratory ↔ Confirmatory",
       y = "Posterior Probability",
       caption = "P(E|H) = .8, P(H) = .1") +
  NULL
p
```

```{r}
p +
  scale_x_continuous(limits = c(.8, 1)) +
  NULL
```
